\documentclass{report}

\author{32pounds}

\begin{document}
    \title{Homework 3 LaTeX Documentation}
    \maketitle
    \clearpage
    \chapter{Combat}
    Summary: When any player or NPC is fighting one another.\\
    
    Steps:
    \begin{enumerate}
        \item Intiation or Agro.
        \item Cool down on current attack begins.
        \item Damage is taken and delt, totals for these values are deducted from health.
        \item If either player or NPC has zero health the combat ends.
    \end{enumerate}
    
    \section{Intiation and Agro}
    Summary: Player strikes other party to begin combat or agro, when the player becomes too close to an agressive NPC.\\
    Preconditions: Two parties are within striking distance of each other. % Look into map/movement for intiation.
    
    \section{Cooldown}
    Summary: The minimum amount of time a player must wait after using an weapon/ability again. The duration of cooldown is based off of the weapon/ability used..\\ % See weapon swapping
    Preconditions: Player has used an weapon/ability.\\
    
    \begin{enumerate}
        \item Cooldown starts.
        \item Cooldown ends after preset amount of time.
    \end{enumerate}
    Alternative: Player swapped weapon/ability while cooldown was active, thus reseting cooldown. \textit{See weapon swapping.}

    \section{Damage}
    Summary: The amount of hitpoints to decrement from the player or NPC's health. This varies between weapons and abilities.\\
    
    Preconditions: Stike must have landed on target.
    
    Alternative: The attack does not hit the intended target and instead misses.\textit{See Missing.}
    
    \section{Missing}
    Summary: When a player launches an attack and the attack doesn't land on the target.\\
    
    Preconditions: The player must have intiated an attack or as been attacked through agro.\\
    Alternative: The attack lands on intended target. \textit{See Damage}
\begin{chapter}{Player Class Summary}
 Upon starting the game, the user is assigned a base character(sales) for level 1 (training). After completion of level 1 the user may now choose between the following class of characters: Accountant(Heavy) -- IT(Distance) -- HR(Mage) -- Sales (Base).  Every class has four attributes with one attribute that caters specifically each class.\\ 
\begin{itemize}
\item \textbf{Strength} which is specialized to Accountants\\ 
\item \textbf{Speed} which is specialized to Sales\\ 
\item \textbf{Focus} which is specialized to IT\\ 
\item \textbf{Synergy} which is specialized to HR\\  
\end{itemize}
Specialization to each character makes upgrading attributes cheaper/easier for that character.\\

\textbf{\large{Accountant}}
\begin{itemize}
  \item Weapon: Roll of Quarters
  \item Miss percent: Constant with specialization -- High miss percentage with non-specialization weapon
  \item Cooldown Time: Standard (1 second) -- lowers with level increase % see player use cases
  \item An increase in Power Attribute -- Increase in Strike damage \\
\end{itemize}

\textbf{\large{IT}} 
\begin{itemize}
  \item Weapon: Floppy Disc Toss
  \item Miss percent: Low with specialization - High miss percentage with non-specialization weapon
  \item Cooldown Time: Average (1.5 seconds) -- lowers with level increase
  \item An increase in Focus Attribute -- Increase in disc toss accuracy (miss percent lowers)\\
\end{itemize}

\textbf{\large{HR}}
\begin{itemize}
  \item Weapon: Wand Pen (Spells)
  \item Miss percent: Constant with specialization - High miss percentage with non-specialization weapon
  \item Cooldown Time: High (2 seconds) -- lowers with level increase
  \item An increase in Synergy Attribute -- Increase in spell duration\\
\end{itemize}

\textbf{\large{Sales}}
\begin{itemize}
  \item Weapon: Stapler
  \item Miss percent: Constant with specialization - high miss percentage with non-specialization 
  \item Cooldown Time: Low (.5 seconds) -- lowers with level increase
  \item An increase in Speed attribute -- decrease in cooldown time
\end{itemize}
\end{chapter}


\end{document}
