\begin{chapter}{Project Requirements}
When we were designing the game we were given a set of requirements that were our system requirements for the game that we were to implement. From these requirements, we chose the ones that were the most important for the time that we had available for design implementation and pushed those to the front of our backlog.  

\begin{section}{Client Requirements}
	\begin{itemize}
		\item Plays as a standalone single player game
		\item Allows for multiplayer with up to 27 players
		\item Starts with a main menu that will launch the game
		\item Allows the player to launch a new game, load a saved game, save a game and join an existing game
		\item Plays on a 2-D tile-based map
		\item Implement player actions including: move, chat, buy/sell/trade, do work
		\item Use an ASCII text file to implement the level art
		\item Implement either a full-real time or semi-real time system
		\item Implement a skill tree for players to develop after level one as they gain higher levels.
		\item NPC interaction that allows for the player to gain NPC party members by achieving a certain amount of faction points.
		\item Allows the player to backtrack through levels that they have already beaten, i.e not have to clear all the NPCs/Monsters in previously beaten levels
		\item Implements 4 levels: Basic office, Spaceport America, Space Station, and Cyberspace.
	\end{itemize}
\end{section}

\begin{section}{Implemented Requirements}
	\begin{itemize}
		\item Plays as a standalone single player game
		\item Allows for wireless networked multiplayer gameplay.
		\item Players can join an existing game by hitting join game and entering the IP address of the hosting entity.
		\item Allows the player to launch a new game, host a game or join an existing game.
		\item Plays on a 2D tile based map
		\item Runs as a full-real time system
		\item Uses ASCII based character files for implementing the tile art.
		\item Implement several different monster AIs.
		\item Allows the player to traverse through 2-3 different levels: office space, space station and the mysterious cyberspace level, which the player cannot access without special access.
	\end{itemize}
\end{section}
\end{chapter}
