\begin{subsection}{Player Movement}
\textbf{Actors}:
Player

\textbf{Goal}:
Simple movement across the map.

\textbf{Preconditions}:
\begin{enumerat}
\item The tile the player is moving to must be walkable.
\item The tile must not be a portal.
\end{enumerate}

\textbf{Summary}:
The player can traverse the level until he/she reaches an obstacle or wall.  

\textbf{Related Use Cases}:
All overworld interactions are extended by this use case. Combat and Level Transfer are examples.

\textbf{Steps}:
\begin{enumerate}
\item The player chooses a direction designated by the movement keys.
\item The input handler checks to see if the move is legal.
\item The player continues to move around the area until an obstacle or wall is reached.
\end{enumerate}
\end{subsection}

\begin{subsection}{Level Transfer}
\textbf{Actors}:
Player

\textbf{Goal}:
Transportation from level 1 to level 2.

\textbf{Preconditions}:
\begin{enumerat}
\item The tile the player is moving from must be walkable.
\end{enumerate}

\textbf{Summary}:
The player has found the portal tile and would like to tranfer to or from each level

\textbf{Related Use Cases}:
Player Movement

\textbf{Steps}:
\begin{enumerate}
\item The player chooses a direction designated by the movement keys.
\item The input handler checks to see if the move is legal.
\item The player moves to a transport tile.
\item The input handler checks to see if the transport tile is vacant.
\item The player is moved to the next/previous level.
\end{enumerate}
\end{subsection}

\begin{subsection}{Combat}
\textbf{Actors}:
Player(s), Enemy Entity(-ies)

\textbf{Goal}:
The Player encounters an enemy and starts combat.

\textbf{Preconditions}:
\begin{enumerate}
\item The Player and entity have tried to access the same tile. 
\end{enumerate}

\textbf{Summary}:
Either the player or entity have collided, depending on the entity, the player either lives
or dies.

\textbf{Steps}:
\begin{enumerate}
\item If the player is stronger than the entity, the entity will die.
\item Players score will be incremented by 1 point.
\end{enumerate}

\textbf{Alternatives}:
\begin{enumerate}
\item If the entity is stronger than the player, the player will die.
\item Players score will be recorded.
\item Player will return to Main Menu Screen.
\end{enumerate}
\end{subsection}

