\begin{subsection}{Speak with NPC}
\textbf{Actors}:
Player, NPC

\textbf{Goal}:
Player wishes to speak with an NPC in order to gain information or recieve 
a quest.

\textbf{Preconditions}:
\begin{enumerate}
\item The player is adjacent to an NPC.
\item The NPC has an available speak interact command
\end{enumerate}

\textbf{Summary}:
The player communicates with an NPC that is occupying the nearby space 
in the world. Communication will add new game information and/or start
a new quest.

\textbf{Related Use Cases}:
This use case extends the Interact with Coworker use case, and will be 
connected to use cases coorelating to interacting with NPCs through 
dialog.

\textbf{Steps}:
\begin{enumerate}
\item Player selects NPC to interact with
\item Player selects the speak function from the interact menu
\item Information is written to the screen
\item If necessary, input will be selected from options on the screen
	to allow player to respond to NPC.
\end{enumerate}
\end{subsection}



\begin{subsection}{Picking Up/Placing Items in Inventory}
\textbf{Actors}:
Player

\textbf{Goal}:
Player wishes to move item from world space into their inventory.

\textbf{Preconditions}
\begin{enumerate}
\item Player occupies space with object
\item Player has an empty slot in their inventory
\end{enumerate}

\textbf{Summary}:
The player comes into contact with an object within the world 
space, moves it from the world space to their inventory.

\textbf{Related Use Cases}:
This use case extends the World Entity Interaction use case, and the
use case upgrading items extends from it.

\textbf{Steps}:
\begin{enumerate}
\item Player moves to the same space as a visible object occupying world
	space.
\item Player selects the place object in inventory selection from 
	interaction menu.
\item Object appears in single slot of players inventory.
\item Object is removed from the world space.
\end{enumerate}

\textbf{Alternatives}:
Player does not have an empty slot in their inventory, no action is
taken (see \textit{Preconditions}).
\end{subsection}
\end{section}



\begin{subsection}{Movement through Area}
\textbf{Actors}:
Player

\textbf{Goal}:
To cross the current area and enter the next one.

\textbf{Preconditions}:
\begin{enumerate}
\item The tile the player is moving to must not have an obstacle. 
\item If there is an item required to move on to the next area, the player must possess it.
\end{enumerate}

\textbf{Summary}:
The player will traverse across an area until an exit tile is reached. If he/she encounters a wall or solid object, they player will not move in the direction of the obstacle. When the player stands on an exit tile, the will move to an new area.

\textbf{Related Use Cases}:
All overworld interactions are extended by this use case. Talking to npcs, combat, and picking up items are examples.

\textbf{Steps}:
\begin{enumerate}
\item The player chooses a direction designated by the movement keys.
\item The input handler checks to see if the move is legal.
\item The player continues to move around the area until an exit tile is reached.
\item The player moves onto the exit tile to take him/her to the next areal.
\end{enumerate}
\end{subsection}



\begin{subsection}{Engage Combat}
\textbf{Actors}:
Player(s), Enemy Entity(-ies)

\textbf{Goal}:
The Player encounters an enemy and starts combat.

\textbf{Preconditions}:
\begin{enumerate}
\item The Player is adjacent to the Enemy Entity.
\item The Player has the Combat flag enabled.
\item The Enemy Entity has the Combat flag enabled.
\end{enumerate}

\textbf{Summary}:
The Player engages in combat with an Enemy Entity occupying space in the
World. Combat is carried out in Turns, with each combatant selecting a Move
each Turn, which are then resolved in order from the entity with the
highest Speed value to the entity with the lowest Speed value. When every
member of one side has their Health reduced to 0, then the other side is
victorious. If the Player(s) won, then go to use case \textit{Player
Victory}. If the Player(s) lost, then go to use case \textit{Player Death}.

\textbf{Related Use Cases}:
This use case is a parent to \textit{Combat Turn}. The use cases
\textit{Player Wins Battle} or \textit{Player Death} immediately follow. This
use case can be optionally extended to allow for alternate forms of combat.

\textbf{Steps}:
\begin{enumerate}
\item The Player inputs the Begin Combat command, \textit{or} the Enemy
Entity begins combat with the Player.
\item The System disables the Player's Combat flag.
\item The use case Cmbat Turn is now performed.
\end{enumerate}
\end{subsection}



\begin{subsection}{Combat Turn}
\textbf{Actors}:
Player(s), Enemy Entity(-ies)

\textbf{Goal}:
The Player seeks to reduce the Enemy Entity's Health to 0 and keep their
own Health above 0.

\textbf{Preconditions}:
\begin{enumerate}
\item The Player is currently in the \textit{Engage Combat} use case.
\item The Enemy Entity is currently in the \textit{Engage Combat} use case.
\end{enumerate}

\textbf{Summary}:
The Player and the Enemy Entity both select a Move. Moves are then
sequentially executed, with the Move selected by the Entity with the
largest Speed value being evaluated first, and the Move selected by the
Entity with the smallest Speed value being evaluated last.

\textbf{Related Use Cases}:
This use case is a child of the \textit{Engage Combat} use case, and can be
optionally extended to provide alternative combat mechanics.

\textbf{Steps}:
\begin{enumerate}
\item The System prompts the Player with a list of legal Moves.
\item The Player selects a Move.
\item The Enemy entity selects a Move.
\item The System evaluates all Moves, in order of Speed.
\item The System updates the state of each Entity as appropriate.
\item If the Enemy Entity has a Health of 0, go to use case \textit{Player
	Victory}.
\item If the Player has a Health of 0, go to use case \textit{Player
	Death}.
\end{enumerate}
\end{subsection}

\textbf{Steps}:
\begin{enumerate}

\item \label{combat:turn} Perform use case \textit{Combat Turn}.
\item If neither side has been reduced to 0 Health,
	go to step \ref{combat:turn}.
\item If the Enemy Entity has a Health of 0, go to use case \textit{Player
	Victory}.
\item If the Player has a Health of 0, go to use case \textit{Player
	Death}.
\end{enumerate}
\end{subsection}



\begin{subsection}{Player Wins Battle}
\textbf{Actors}:
Player(s), Enemy Entity(-ies)

\textbf{Goal}:
The Player seeks to list and distribute the benefits of victory.

\textbf{Preconditions}:
\begin{enumerate}
\item The Player is currently in the \textit{Combat Turn} use case.
\item The Player has a Health which is greater than 0.
\item The Enemy Entity is currently in the \textit{Combat Turn} use case.
\item The Enemy Entity has a Health of 0.
\item The \textit{Combat} use case is requesting for the \textit{Player
	Victory} use case to be run.
\end{enumerate}

\textbf{Summary}:
The Player is informed of any Items or Reputation gained. If multiple
Players are present, then they reach an agreement on how the Items are to
be distributed.

\textbf{Related Use Cases}:
This use case can only be begun when transitioning from the \textit{Combat Turn}
use case.

\textbf{Steps}:
\begin{enumerate}
\item The System calculates the Items and/or Reputation gained by the
	Player based upon the Enemy Entity.
\item The System informs the Player of the Items and/or Reputation gained.
\item If there is only one player, go to step \ref{player_victory:end}.
\item \label{player_victory:distribute_items} The System allows the Players
to distribute the Items gained.
\item The Players either agree or do not agree to the distribution.
\item If the Players do not agree,
	go to step \ref{player_victory:distribute_items}
\item \label{player_victory:end} Go to use case \textit{Place Items in
	Inventory}.
\end{enumerate}
\end{subsection}
\end{section}



\begin{subsection}{Inventory Item Use}

\textbf{Actors}:
Player, Inventory, Useable Item

\textbf{Preconditions}:
\begin{enumerate}
\item Inventory belongs to Player.
\item Item is in Inventory.
\item Item is useable from the Inventory
\item Player inputs the use command, selecting Item for use.
\end{enumerate}

\textbf{Summary}:
The Player uses the Item in their Inventory. The Item produces its
use effect.

\textbf{Related Use Cases}
All Useable Item Uses extend this use case. Examples would be quaffing
a potion or reading a note.

\textbf{Steps}:
\begin{enumerate}
\item Player selects Item from Inventory.
\item System enables the input of the use command.
\item Player inputs the use command.
\item System evaluates the effect of the use command on the
Useable Item and updates the Item's state accordingly.
\end{enumerate}
\end{subsection}



\begin{subsection}{Interact with a Coworker}
\textbf{Actors}:
Player, NPC

\textbf{Goal}:
The Player wishes to perform an interaction with an NPC.

\textbf{Preconditions}:
\begin{enumerate}
\item The Player is adjacent to the NPC.
\end{enumerate}

\textbf{Summary}:
The Player interacts with an NPC occupying space in the World. The
interaction may or may not cause a state change for either the Player or
the NPC relationship.

\textbf{Related Use Cases}:
All specific NPC interactions extend this use case. Examples include
modifying a relationship or managing quests.

\textbf{Steps}:
\begin{enumerate}
\item The Player inputs the interact command, selecting the NPC.
\item The System performs the interaction, gathing additional input from the
	Player as necessary.
\end{enumerate}



\begin{subsection}{World Entity Interaction}

\textbf{Actors}:
Player, Interactable Entity

\textbf{Preconditions}:
\begin{enumerate}
\item Player is adjacent to the Interactable Entity.
\item Player inputs the interact command, selecting the Interactable Entity.
\end{enumerate}

\textbf{Summary}:
The Player interacts with the Entity occupying space in the World. The Entity 
produces its interactive effect. 

\textbf{Related Use Cases}
All World Entity Interactions extend this use case. Examples would be 
opening a door or operating a switch.

\textbf{Steps}:
\begin{enumerate}
\item Player moves adjacent to an Interactable Entity.
\item System enables the input of the interact command.
\item Player inputs the interact command.
\item System evaluates the effect of the interact command on the
Interactable Entity and updates the Entity's state accordingly.
\item Player moves away from the Interactable Entity.
\item System disables the input of the interact command.
\end{enumerate}
\end{subsection}